Technical Report

### 2017-11-24 fully-abstract-comp/technical-report.tex
Removed two lines from the memory satisfaction definition. We will reintroduce them if we need them.
Added a frame to the observation relation.
Updated the K, R (and P) relation
P had a couple of typos.
K now assumes fewer things.
R is now indexed with a set R of registers that are not taken into consideration as K and E has different needs.
Typo in memSat, changed P-LR to take list, specified what we mean by R being a separation of W in R-relation.
wrote up some suggestions for updates of V-relation based on chat with Lars

\newcommand{\nsubeq}[1][n]{\overset{#1}{\subseteq}}
\newcommand{\nsupeq}[1][n]{\overset{#1}{\supseteq}}

@@

@@

\subsection{Memory satisfaction}
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \exists R_\ms : \dom(W) \fun \MemSeg^2 \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(W)} \pi_2(R_\ms(r)) \wedge \\
      \quad \stk = (\_,\ms_{\stk,0}) :: \dots :: (\_,\ms_{\stk,m}) \wedge \\
      \quad \exists r_0 , \dots, r_m, r_{m+1} \ldotp \pi_1(R_\ms(r_0,\dots,r_m)) = \ms_{\stk,0},\dots , \ms_{\stk,m} \wedge \\
      \qquad \pi_1(R_\ms(r_{m+1})) = \ms_\stk \wedge \\
      \qquad \ms_S \uplus \ms_\stk \uplus \ms_{\stk,0} \uplus \dots \ms_{\stk,m} = \biguplus_{r \in \dom(W)} \pi_1(R_\ms(r)) \wedge \\
      \qquad \exists R_w : \dom(W) \fun \World \ldotp\\
      \quad \qquad W = \bigoplus_{r \in \dom(W)} R_w(r) \wedge \\
      \quad \qquad \forall r \in \dom(W) , n' < n \ldotp \\
      \qquad \qquad \npair[n']{R_\ms(r)} \in W(r).H \; (W(r).s) \; (\xi^{-1} (R_w (r))) 
    \end{array}
  \right.
\]
In the definition of memory satisfaction, $R_\ms$ creates a partitioning of the two related memories. As the source language is a special interpretation of the target language, part of the target memory needs to relate to the stack in the source language. We also need to split up the world which is done by $R_W$.We split up the world in order to make sure that the linearity constraints imposed by the world are satisfied.
\lau{30-10-2017: It is not clear to me whether this definition should also talk about $\opc$.}

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrk, W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair[.]{k_{c,S},k_{d,S}}{k_{c,T},k_{d,T}}} \in \lrk(W_\lrk) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,S},v_{d,S},k_{c,S},k_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,T},v_{d
,T},k_{c,T},k_{d,T}})\endarray\right)}
      \in \lro(W\oplus W_\lrk \oplus W_\lrr \oplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "spatial" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfaction does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}

\[
  \lro(W) = \left\{ \npair{\left(\array{l}\src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})},\\(\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \forall i \leq n \ldotp \\
      \quad \src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\ms_T,\reg_T) \term\\
      \quad \tand\\
      \quad (\ms_T,\reg_T) \term[i] \Rightarrow \src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

\lau{03-11-2017: TODO take a look at linearity of this definition - in particular the recovered pc and stack pointer.}

\[
  \lrk(W) = \left\{ \npair{\left(\array{l}\src{\retptrc(\sigma,(\perm,\lin,\baddr_c,\eaddr_c,\aaddr_c))},\\\src{\retptrd(\sigma,(\aaddr_d,\eaddr_d))},\\k_{c,T},k_{d,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} = \sealed{\sigma,c_d} \wedge\\
      k_{c,T} = \sealed{\sigma,c_c} \wedge\\
      c_c = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c) \wedge\\
      c_d = ((\rw,\linear),\aaddr_d,\eaddr_d,\aaddr_d-1) \wedge\\
      \npair[n]{\stpair[.]{\retptrc(\sigma,\_)}{k_{c,T}},\stpair[.]{\retptrc{\retptrd(\sigma,\_)}}{k_{d,T}}} \in \lrp(W) \wedge \\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall W_\lrr, W_\lrm \ldotp  \\
      \qquad\opc = c_c \wedge\\
      \qquad\dom(\ms_{\stk,f}) = [\aaddr_d,\eaddr_d] \wedge\\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk::(\opc,\ms_{\stk,f}),\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \qquad\src{reg_S}(\rstk) = \src{\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\_}} \wedge \\
      \qquad\eaddr_\stk = \aaddr_d-1\\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{\left(\arraycolsep=0pt\array{l}\ms_S,\reg_S\updReg{\pcreg,\rstk}{\opc,\stkptr{\rw,\baddr_\stk,\eaddr_d,\aaddr_d}},\\\stk, \ms_\stk \uplus \ms_{\stk,f}\endarray\right)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rstk}{\opc,((\rw,\lin),\baddr_\stk,\eaddr_d,\aaddr_d)})\endarray\right)}
      \in \lro(W' \oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}
\]

\[
  \lrp(W) = \left\{
    \npair{\stpair[.]{c_1}{c_1'}\stpair[.]{c_2}{c_2'}} \middle| 
    \begin{array}{l}
      \text{for $i \in \{1,2\}$} \\
      \src{\baddr_i} = \pi_\baddr(\src{c_i}) \wedge \src{\eaddr_i} = \pi_\eaddr(\src{c_i}) \wedge 
      \baddr_i' = \pi_\baddr(c_i') \wedge \eaddr_i' = \pi_\eaddr(c_i') \wedge \\
      \src{\lin_i} = \pi_\lin(\src{c_i}) = \pi_\lin(c_i') \\
      \quad \exists r \in \addressable{l,W} \ldotp\\
      \qquad \forall \npair{n}{\stpair{\ms}{\ms}} \in W(r).H \; W(t).s \xi^{-1}(W)  \ldotp \\
      \qquad \quad \dom(\src{\ms_S}) \subseteq [\src{\baddr_i},\src{\eaddr_i}] \wedge \dom(\ms_T) \subseteq [\baddr_i',\eaddr_i']      
    \end{array}
  \right\}
\]

\[
  \lrr(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad S \text{ is a separation of $W$} \tand\\
      \quad \forall r \in \RegName \setminus \{\pcreg, \rretd,\rretc,\rdata \}\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).

\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\_)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \;\middle| \;
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrd(\sigma,\_)}{\sealed{\sigma,\vsc_D}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\retptrc(\sigma,\_),\retptrd(\sigma,\_),\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\_)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \;\middle| \;
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}

    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} \;\middle|\;
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{r l l }
      \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W}\\
      \perm = \rwx &\Rightarrow& \npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}\\
      \perm = \rx &\Rightarrow& \npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}
    \end{array}

@@

\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall n' < n, W' \privft W, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr] \ldotp\\
      \quad \forall W'', c_{d,S},c_{d,T} \ldotp \npair[n']{\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lrv(W'') \wedge \\
      \qquad \npair[n']{((\perm,lin),\baddr,\eaddr,\aaddr),c_{d,S},((\perm,lin),\baddr,\eaddr,\aaddr),c_{d,T}} \in \lrp(W' \oplus W'') \Rightarrow \\
      \quad \qquad \npair[n']{\stpair[.]{((\perm,lin),\baddr,\eaddr,\aaddr)}{((\perm,lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lre(W' \oplus W'')
    \end{array}
    \right\}
\]

>>>>

\newcommand{\nsubeq}[1][n]{\overset{#1}{\subseteq}}
\newcommand{\nsupeq}[1][n]{\overset{#1}{\supseteq}}
\newcommand{\nequal}[1][n]{\overset{#1}{=}}

@@

%%% Regions
\newcommand{\stdreg}[2]{\iota^{\mathrm{std},#2}_{#1}}
\newcommand{\stareg}[2][\stpair{\ms}{\ms}]{\iota^{\mathrm{sta},#2}_{#1}}
\newcommand{\spa}{\mathrm{s}}
\newcommand{\spao}{\mathrm{so}}
\newcommand{\pur}{\mathrm{p}}

@@

\subsection{Memory satisfaction}
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \exists R_\ms : \dom(W) \fun \MemSeg^2 \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(W)} \pi_2(R_\ms(r)) \wedge \\
      \quad \stk = (\_,\ms_{\stk,0}) :: \dots :: (\_,\ms_{\stk,m}) \wedge \\
      \quad \ms_S \uplus \ms_\stk \uplus \ms_{\stk,0} \uplus \dots \uplus \ms_{\stk,m} = \biguplus_{r \in \dom(W)} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_w : \dom(W) \fun \World \ldotp\\
      \qquad W = \bigoplus_{r \in \dom(W)} R_w(r) \wedge \\
      \qquad \forall r \in \dom(W) , n' < n \ldotp \\
      \quad \qquad \npair[n']{R_\ms(r)} \in W(r).H \; (W(r).s) \; (\xi^{-1} (R_w (r))) 
    \end{array}
  \right.
\]
In the definition of memory satisfaction, $R_\ms$ creates a partitioning of the two related memories. As the source language is a special interpretation of the target language, part of the target memory needs to relate to the stack in the source language. We also need to split up the world which is done by $R_W$.We split up the world in order to make sure that the linearity constraints imposed by the world are satisfied.
\lau{30-10-2017: It is not clear to me whether this definition should also talk about $\opc$.}

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrk, W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair[.]{k_{c,S},k_{d,S}}{k_{c,T},k_{d,T}}} \in \lrk(W_\lrk) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rretd,\rretc,\rdata\})(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,S},v_{d,S},k_{c,S},k_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,T},v_{d
,T},k_{c,T},k_{d,T}})\endarray\right)}
      \in \lro(W\oplus W_\lrk \oplus W_\lrr \oplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "spatial" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfaction does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}

\[
  \lro(W) = \left\{ \npair{\left(\array{l}\src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})},\\(\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \forall i \leq n, \src{\ms_{f,S}}, \ms_{f,T} \ldotp \\
      \quad \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\ms_T \uplus \ms_{f,T},\reg_T) \term\\
      \quad \tand\\
      \quad (\ms_T \uplus \ms_{f,T},\reg_T) \term[i] \Rightarrow \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

\[
  \lrk(W) = \left\{ \npair{\left(\array{l}\src{\retptrc(\sigma,(\perm,\lin,\baddr_c,\eaddr_c,\aaddr_c))},\\\src{\retptrd(\sigma,(\aaddr_d,\eaddr_d))},\\k_{c,T},k_{d,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} = \sealed{\sigma,c_d} \wedge\\
      k_{c,T} = \sealed{\sigma,c_c} \wedge\\
      c_c = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c) \wedge\\
      c_d = ((\rw,\linear),\aaddr_d,\eaddr_d,\aaddr_d-1) \wedge\\
      \npair[n]{[\stpair[.]{\retptrc(\sigma,\_)}{k_{c,T}},\stpair[.]{\retptrd(\sigma,\_)}{k_{d,T}}]} \in \lrp(W) \wedge \\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall W_\lrr, W_\lrm \ldotp  \\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk::(\opc,\ms_{\stk,f}),\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \qquad\opc = c_c \wedge\\
      \qquad\dom(\ms_{\stk,f}) = [\aaddr_d,\eaddr_d] \wedge\\
      \qquad\npair[n']{\array{l}\src{\reg_S\update{\rstk}{\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}}},\\
                               {\reg_T\update{\rstk}{((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)}}\endarray}\in \lrr(\{r_\stk\})(W_\lrr) \wedge\\ 
      \qquad\npair[n']{[(\opc,\opc)]} \in \lrp(W')\\
      \qquad\Rightarrow\\
      \qquad \npair[n']{\left(\arraycolsep=0pt\array{l}
                          \left(\arraycolsep=0pt\array{l}
                            \src{\ms_S,\reg_S\update{\pcreg,\rstk}{\opc,\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}},}\\
                            \src{\stk, \ms_\stk \uplus \ms_{\stk,f}}
                          \endarray \right) \\
                          \left(\ms_T,\reg_T\update{\pcreg,\rstk}{\opc,((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)} \right)
                        \endarray \right)} \in \lro(W'\oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}
\]

\[
  \lrp(W) = \left\{
    \npair{ \overline{\stpair[.]{c}{c'}} } \middle| 
    \begin{array}{l}
      \text{for $\stpair[.]{c}{c'} \in \overline{\stpair[.]{c}{c'}}$} \\
      \src{\baddr} = \pi_\baddr(\src{c}) \wedge \src{\eaddr} = \pi_\eaddr(\src{c}) \wedge 
      \baddr = \pi_\baddr(c) \wedge \eaddr = \pi_\eaddr(c) \wedge \\
      \src{\lin} = \pi_\lin(\src{c}) = \pi_\lin(c) \\
      \quad \exists r \in \addressable{l,W} \ldotp\\
      \qquad \forall \npair{\stpair{\ms}{\ms}} \in W(r).H \; W(r).s \; \xi^{-1}(W)  \ldotp \\
      \qquad \quad \dom(\src{\ms_S}) \subseteq [\src{\baddr},\src{\eaddr}] \wedge \dom(\ms_T) \subseteq [\baddr,\eaddr]      
    \end{array}
  \right\}
\]

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad W = \bigoplus_{r \in \RegName} S(r) \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
\lau{TODO: Rewrite the other definitions to pass around $H_\sigma$ (if this is how we want to handle seals.)}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\_)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \;\middle| \;
    \begin{array}{l}
%      \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrd(\sigma,\_)}{\sealed{\sigma,\vsc_D}}} \in \lrv(W_\lrv) \ldotp\\
%      \npair[n']{\retptrc(\sigma,\_),\retptrd(\sigma,\_),\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\baddr,\eaddr)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_D = ((\rw,\linear),\baddr,\eaddr,\baddr-1) \wedge\\
      \exists r \in \addressable{\linear,W} \ldotp \\
      \quad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \dom(\ms) = [\baddr, \eaddr] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \forall W' \privft W \ldotp \\
      \qquad \quad \exists r' \ldotp W'(r') = W(r) \wedge \exists r'' \ldotp W'(r'') = \stdreg{[\stkb,\aaddr]}{\spao} \ldotp \\
      \qquad \qquad { \color{red} \forall (c, c') \in H_\sigma (\sigma) \ldotp \npair{\src{c,\retptrd(\sigma,\baddr,\eaddr)}, c' , \sealed{\sigma,\vsc_D}} \in \lrk(W') }%\text{\lau{This needs some work - specifically what i c and c' and do we need to seal them?}}

%    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W_\lrv) \ldotp\\
%      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \stpair{\vsc}{\vsc} \in H_\sigma \; \sigma \wedge \\
      \forall \stpair{\vsc'}{\vsc'} \in H_\sigma \; \sigma \ldotp \\
      \quad \npair{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lre(W) \wedge \\
      \quad \npair{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lre(W)
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{r l l}
      \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\linear,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\linear,W}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{r l l }
      \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W}\\
      \perm = \rwx &\Rightarrow& \npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}\\
      \perm = \rx &\Rightarrow& \npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}
    \end{array}

@@

\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall n' < n, W' \privft W, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr] \ldotp\\
      \quad \forall W'', c_{d,S},c_{d,T} \ldotp \npair[n']{\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lrv(W'') \wedge \\
      \qquad \npair[n']{[\stpair[.]{((\perm,lin),\baddr,\eaddr,\aaddr)}{((\perm,lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}]} \in \lrp(W' \oplus W'') \Rightarrow \\
      \quad \qquad \npair[n']{\stpair[.]{((\perm,lin),\baddr,\eaddr,\aaddr)}{((\perm,lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lre(W' \oplus W'')
    \end{array}
    \right\}
\]
